\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{fontspec} % Required for specifying fonts
\usepackage{polyglossia} % For multilingual support
\usepackage{hyperref}
\setmainlanguage{english} % Set the main language to English
\setotherlanguage{arabic} % Specify Arabic as the secondary language
\newfontfamily\arabicfont[Script=Arabic]{Amiri} % Specify an Arabic font
\setlength{\parskip}{1em} % Adjust this value as needed


\hypersetup{
    pdfauthor={Nouman Ali Khan},     % Author of the document
    pdftitle={Dialogs in the Quran},    % Title of the document
    pdfkeywords={quran, nouman, dialogs}, % List of keywords
    pdfproducer={LaTeX with hyperref}, % Producer of the document
    pdfcreator={pdflatex} % Creator of the document
}

% Commands
\newcommand{\as}{\textarabic{(عليه السلام)}}

\title{Dialogs in the Quran}
\author{Nouman Ali Khan}
\date{\today}

\begin{document}

\maketitle

\emph{This document has been transcribed using OpenAI whisper which is automatic speech recognition (ASR) and edited from} \footnote{The original source can be found at \url{https://www.youtube.com/watch?v=h-TYtoBXb_I}}\emph{. The edits primarily focused on removing discourse markers or fillers to enhance readability and ensure the information is suitable for written format.}

\section*{Musa\as{} and Firaun}


\textarabic{الحمد لله} 

In order to give you a sample of how beautiful and how powerful dialog in the Quran is, I'll tell you a story. The dialog I have chosen to share with you at is a dialogue that takes place between Musa\as{} and Firaun. I'll start you off. 

\textarabic{أعوذ بالله من الشيطان الرجيم} 

\textarabic{وَإِنَّ رَبَّكَ لَهُوَ ٱلْعَزِيزُ ٱلرَّحِيمُ} 

\textit{"No doubt about it. Your Master truly is the ultimate authority. And truly he is always loving and caring"}. 

Allah's authority will manifest against Firaun and Allah's loving care will be on the side of Musa\as{}.  

\textarabic{وَإِذْ نَادَىٰ رَبُّكَ مُوسَىٰٓ أَنِ ٱئْتِ ٱلْقَوْمَ ٱلظَّـٰلِمِينَ} 

\textit{"When your Master made a call to Musa, go to the wrongdoing nation"}.

Musa\as{} is now being called. Where is Musa\as{}? On top of the mountain. He's having a conversation with Allah. That's where we are beginning in Surah Ash-Shu'ara, Surah number 26. And Allah is saying to him, you need to go to the wrongdoing nation. Now Allah is not telling him to go to one person. He's going to tell him to go to the entire nation. Which wrongdoing nation, ya Allah? He says, 

\textarabic{قَوْمَ فِرْعَوْنَ ۚ أَلَا يَتَّقُونَ} 

\textit{"The nation of Firaun, don't they have any taqwa?"} 

You need to go to the nation of Firaun. The problem with that is Musa\as{} is a fugitive, wanted for murder running away from where? \dots from Firaun. And he needs to go back and not just go talk to one person. He needs to go talk to the entire nation. I need you to understand the irony here. As he left Egypt, he made sure not a single person saw him. And as he goes back, he has to make sure he sees every single person. He needs to go address the entire nation. That's the responsibility Allah has given him. 

\textarabic{قَوْمَ فِرْعَوْنَ ۚ أَلَا يَتَّقُونَ}, 

\textit{don't they have any fear? don't they have any fear?}

Now Musa\as{} is going to respond to this. 

\textarabic{ قَالَ رَبِّ إِنِّىٓ أَخَافُ أَن يُكَذِّبُونِ} 

\textit{"He said, Master, I am really afraid that they will call me a liar"}. 

His fear number one, what is it? They will call me a liar. Fear number two,

\textarabic{وَيَضِيقُ صَدْرِى}. 

\textit{"My chest becomes tight"}
   
Let me tell you what that means. Musa\as{} is a hot temper. He gets angry sometimes. And when they call him a liar, he will become what? \dots angry. And when his anger comes in, his chest becomes tight. 

\textarabic{وَيَضِيقُ صَدْرِى} 

\textit{"I get frustrated"}. You can say, I get frustrated. 

\textarabic{وَلَا يَنطَلِقُ لِسَانِى} 

\textit{"And my tongue stops moving"}
   
I get frustrated and my tongue stops moving. So if you got three problems so far, one, they will call me a liar. Two, I get frustrated. Three, my tongue stops moving. You need to understand what that means. When a person gets frustrated, they can't speak anymore. I know that's true of me. When I'm really, really angry, I'm not able to even make one clear sentence. I start jumbling my words. \textarabic{والله}, I sound like I don't know how to speak. 
   
I sound like I don't know how to speak when I'm really frustrated. That's what I do when I'm frustrated. If I'm not frustrated, I could talk forever. So what my wife tells me. Which is why she really tries to frustrate me. So I talk less. 
   
But anyway, anyway. Now when he gets frustrated, what's going to happen? He won't be able to speak. The other problem is, Musa\as{}, has a stutter. And when people that have a stutter get frustrated, what happens? They can't speak. He says to Allah, Allah, they will call me a liar. I will get frustrated. And my tongue will stop moving. 

\textarabic{وَلَا يَنطَلِقُ لِسَانِى فَأَرْسِلْ إِلَىٰ هَـٰرُونَ} 

\textit{"Then send the mission to Haroon also"} 
   
Send the message to Haroon\as{}  also. In other words, in other places we'll learn in the Quran. Why send it to Haroon\as{} ? If I don't do the job, who will? 

\dots Haroon\as{}  will. 

So so far, what are the problems and requests? 

\begin{itemize}
    \item First problem. They'll call me a liar 
    \item Two, I get frustrated
    \item Three, My tongue won't move
    \item Four, Here's a request. Send, Haroon
    \item Five, \textarabic{وَلَهُمْ عَلَىَّ ذَنۢبٌۭ } \textit{"They have a crime registered against me"}
\end{itemize}

I'm wanted. They have a rap sheet on me. I'm wanted for something. What is that?

\dots murder Isn't it? Accidental murder. But that's what they have against me. 

\textarabic{فَأَخَافُ أَن يَقْتُلُونِ} 

\textit{"Therefore, I am afraid that they will kill me"}.

Because I know last time I was there, my friend told me that as soon as they see me, they're not going to arrest me. They're actually going to kill me. In other words, the cops were not looking for him so they could arrest him. The cops were looking for him so they could kill him. So he says, ya Allah, if I go back, the cops, last I remember, their orders were to see me and not arrest me but see me and kill me. 
Now the list of these five fears, five concerns. That are keeping him from doing his mission. Are in amazing order because if it was me, my first concern would be I am going to get killed. And of this list, where's this concern? It's at the end. His first concern is I will not be able to fulfill your mission. They'll call me a liar. I have a problem. I get frustrated. My tongue doesn't move. The mission is more important than my life. So please send Haroon\as{} . By the way, another reason for sending Haroon\as{}  is I might get killed on sight since they have a crime listed against me. It's like already Musa\as{} recognises that his life is worth nothing compared to the mission that Allah has given him. Allah will respond to him. And Allah says, 

\textarabic{قَالَ كَلَّا ۖ فَٱذْهَبَا بِـَٔايَـٰتِنَآ ۖ إِنَّا مَعَكُم مُّسْتَمِعُونَ }

Here's how I translate 

\textarabic{كَلَّا} 

\textit{"No problem"} 

That's all what Allah says to him. Musa\as{}, given entire speech and Allah says, no problem. It is as though Allah is saying, he says they'll call me a liar. Allah says \textarabic{كَلَّا}. Don't worry about it. But my chest becomes tight. Don't worry about it. My tongue won't move. Don't worry about it. Send Haroon\as{} . Okay, don't worry about it. I gotcha. They have a crime listed against me. Don't worry about it. They might kill me. Don't worry about it. One word done. And this is not like the \textarabic{كَلَّا} you and I use. You know, when you tell your employee, listen. I need you to finish this. This, this, this. You say, what about it? It's so scary to me because that means nothing will get done. Or just like when the sister here tells the husband to get the groceries and he's giving him the list, he goes, no, I don't need the list. Don't worry about it. You know, nothing is coming back. But when Allah says to Musa\as{}, he said, no, no, no, no, no, no, no, no. What is he saying? Everything is taking care of. 
   
Then he says, then both of you go. Hey, wait a second. What do you mean both of you? What is both of you? Who's the two? So in the response, he already includes the response that Musa\as{} has been given authorization to give the mission to Haroon\as{}, also. Go both of you with our miraculous signs. Go with our miracles. Go with our Ayat. Now tell me, did he ask for miracles? So first Allah took care of all of his concerns. Then Allah gave him Haroon. Allah also gave him what he didn't even ask for, which are the miracles. And he says \textarabic{فَأْتِيَا فِرْعَوْنَ فَقُولَآ إِنَّا رَسُولُ رَبِّ ٱلْعَـٰلَمِينَ }. 
   
Here's where he gets so beautiful. He says, no doubt about it. When you go, we are going to be listening alongside you. We're going to be listening along with you. We are going to be listening alongside all of you, not both of you. But it's two of them. Why say all of you? It is as though Allah is saying, I will send a legion of angels with you. They'll be there too. We'll be listening. And it is as though Allah is saying, he won't just be listening to Musa\as{}. He'll be listening to Firaun and the ministers and the Magicians. He'll listen to everybody.  
   
And if Allah is saying that before he even gets us into the conversation, it is as though Allah is telling us, I myself listened to this conversation carefully. What about you? So we better listen to this conversation carefully. That's the legacy left in the Quran by Allah. Then Allah says you know what? Both of you go to Firaun. Wait, wait, wait. I was told to go to the nation. The nation. Now Allah changes it and says, no, no, no. You don't just go to the nation of Firaun. They don't have any taqwa. You need to go straight to who? Firaun, I would think maybe I'll start with the security guards and the farmers. I'll work my way up to the grocery store owner, maybe work with one governor, one minister, work to the second minister. Eventually work my way up. And maybe if I get a chance, I'll talk to who? Firaun. 
   
Allah says, why don't you start with Firaun? That should be easy. You go to Firaun and you tell him, both of you say to him, that we are the messenger, listen, I'm translating carefully. Please tell me where you might think there's an error. We are the messenger of the master of all nations. We are the messenger of the master of all nations. Where's the obvious problem? Not messengers. I'm translating as the ayah says it. Why? Because rhetorically Allah is saying that these two men are supposed to be inseparable. So as though they are not two, but they are one. 
   
Now why is that important? Let me explain in a second. There's lots of things to explain here. Anybody see finding Nemo? Both of you go to Firaun. Tell him that we are the messenger of the master of all nations. And,

\textarabic{أَنْ أَرْسِلْ مَعَنَا بَنِىٓ إِسْرَٰٓءِيلَ} 

\textit{"And you better let the sons of Israel come along with us"} 
   
You better let them go. You go tell him that. Okay? Allah is telling him. And Haroon\as{}. You go tell him that. Okay. 

So you've seen finding Nemo, huh? You better have. So in finding Nemo there's an important scene. Those of you who are not familiar with Islamic history, finding Nemo is extremely important. In finding Nemo, the father whose name is, \dots whose name is? \dots Marlin. Very good. And his blue companion, Dori. Masha'Allah, there are people with, it's not here. Very good. Okay. So, Marlin is depressed. He can't find his son. He ends up on the back of a giant Australian turtle named Crush. And he's really sad. He doesn't want to talk about it. And he says, I'm looking for my son, Nemo, and these baby turtles come and say, really? Tell us the story. Ooh, a story. And he tells them the story. And as he tells them the story, these turtles they swim. And they tell the story to some other fish. Those fish tell it to some other fish. Those fish tell it to some other fish. Those fish jump up. The dolphins jump up and tell it to sea goals. You know those, what? What? What? Like those guys. And then they fly over and get the news to Australia until one of the sea goals years, hey, really? Nemo? His dad's coming. And he flies over to the dentist's office and tells Nemo, right? 

So what I'm trying to say is A told B, B told C, C told D, D told E, E told Nemo, right? Now the story is long. Let's say the story that the fish told, the Marlin told the turtles is 10 sentences. Let's just say it's 10 sentences. How did they film it? How did the filmmakers show the story? They didn't say that between A and B here are the 10 sentences and between B and C, let's repeat those 10 sentences. And between C and D, let's repeat those 10 sentences. They would become extremely boring because we already know those 10 sentences in the story. So they came up with a really creative way of showing you that A told B the story, B told C the story, C told D the story what they did was they showed the first sentence between A and B and the second sentence between B and C and the third sentence between C and D and you can fill in the blanks even a five year old watching the movie can tell that actually it wasn't just one sentence that each party shared. Each party is supposed to have shared what? The entire story but in order to move the story along quickly and get to the interesting parts, this was a technique that was used. 

Now I bring this up because this is a very creative, modern, innovative film technique. No it's not. It's actually in the Quran. It's in the Quran and it's in the story we're about to read. Where is Musa\as{} he's on the mountain. In the light telling him you need to go where? To Firaun is that a short journey or a long journey? And when you go to Firaun you better tell him that we are the messenger of the Master of all nations and you better let the Israelites come along with us. The next ayah says, 

\textarabic{قَالَ أَلَمْ نُرَبِّكَ فِينَا وَلِيدًۭا وَلَبِثْتَ فِينَا مِنْ عُمُرِكَ سِنِينَ ١٨}

Firaun responded. 

\textit{"Didn't I raise you as a newborn? ... "} 

What? Firaun responded. How did we get to Firaun? We just fast forwarded. We were just where? In the movie. On top of the mountain. Great. What's missing? Then Musa\as{} came down from the mountain. It was a sunny day, possibly 12 degrees Celsius. And as he came down northwest, he mounted on his camel, packed his bags, headed towards Haroon\as{} who he hasn't seen for a long time. He sees him, hey Haroon\as{} bro, how's it going? Yeah, did you get the message? Didn't you come to you \dots? Yup, he did. Ready to go, already packed my bags and I got lunch. Your favorite sandwich. Let's go together. Then they went to Egypt. As they got to Egypt, they were kind of worried and they were getting a little hungry. There was a McDonald's on the way but they said that's Haram. So they didn't go there and then they kept going. Now they're inside Egypt and when they're inside Egypt, they're kind of trying to avoid the security guards and they don't know where to go but they remember that Allah told them that they have to go to Firaun which means they had towards the Kafir house, the big castle. They had towards the castle but the castle is not a train station. There are guards outside. You can't just walk in. So they get to the station, they get to the guards outside and the guards stop them. Who's there? And he says Musa, let Firaun know I need to speak with him. The guard goes inside. Firaun is busy inside because he's eating his cheeseburger, trying to catch a fly. Excuse me sir, there's a Musa\as{} here to see you. Musa? Really? Send him in. So the guard comes back outside and tells Musa, hey, you can come in. Musa\as{} says no, Haroon\as{} has to come with me. No, slaves are not allowed inside because Haroon\as{} is from Baniisrail and Baniisrail is considered slaves. Slaves are not allowed inside. Well we're not coming because we are like one. Wait, do you remember hearing that? We are the messenger. We are like we're inseparable. He goes back into Firaun's office. He's making no progress catching the flies. Sir, he's saying that he and his brother have to come in together. Whatever, let him in, let him in. He's probably going to come in and apologize for all those years that he ran away and he's going to ask for his old room back and he's going to ask how I've been and say, sorry, and give me a hug or whatever. Let's see what happens. Let him bring his brother. Maybe he brought me a sacrificial gift. 

Is any of that in the Quran? No, we get straight to the point. We don't even, Allah fast forwards it. Why? Because Allah already said, \textarabic{كَلَّا}, none of that will be a problem. You will get straight to the president of Kufur. You'll have access. You'll have access to the inside of the Oval Office of disbelief. You go on ahead. So now he's inside. And Firaun has now heard. 

Now by the way, when you walk into the court of a king, you're supposed to walk in with humility and you're supposed to praise the king. You're supposed to make him feel good about himself. And of course, if Musa\as{} used to live in that house and he was wanted for murder, he's supposed to walk in and apologize, right? That's the due process of meeting with somebody important. He walks in and he's covered in dirt and he's got his brother with him. He's got a stick in his hand and he walks in and Firaun is up on his throne, looking down on these two men that have no power whatsoever. 

And they walk in and they say, 

\textarabic{فَأْتِيَا فِرْعَوْنَ فَقُولَآ إِنَّا رَسُولُ رَبِّ ٱلْعَـٰلَمِينَ ١٦} 

\textit{"... We are messengers ..."} 

We are two inseparable messengers, you can say it like that. We are two inseparable messengers of the true master of all people's. What? True master? There are generals and there are security guards that are inside this court room and who do they call master? Firaun. And these two walk in and say, we are actually here as representatives of the real master of all nations. Not just another nation, all nation, which means including your nation. So they walk into the king's court and say, actually, you're not the king. And then the second thing they say is, by the way, if you know what's good for you, and \textarabic{أَنْ أَرْسِلْ مَعَنَا بَنِىٓ إِسْرَٰٓءِيلَ ١٧}, you better let the children of Israel come along with us, if you know what's good for you. 

Now what do you think happens to someone who talks like that to Firaun? 

But watch what Firaun does. But before I tell you what Firaun does, I need you to remember something very important, very important. I need you to keep track of what Musa\as{} said. Musa\as{} said that we are a messenger of Allah. We are both the messenger of Allah, of the Rabb. And number two, let who go? Baniisrail go, which means Musa\as{} came with two points. Please don't forget. Musa\as{} walked in with two points, both of which are insulting to Firaun. Who are you to tell me what to do? Walking in here to make a demands. So Firaun turns back to Musa\as{} and says,

\textarabic{قَالَ أَلَمْ نُرَبِّكَ فِينَا وَلِيدًۭا وَلَبِثْتَ فِينَا مِنْ عُمُرِكَ سِنِينَ ١٨} 

\textit{"... Didn't we raise you here as a baby? ..."} 

You talked to me like that? You know an authority who raised you and you were lived in their house and he's putting you in your place? That's how he started. 

\textit{"... didn't you live many years of your life here?"}

You're going to walk in here acting like you own the place? And then he said, 

\textarabic{وَفَعَلْتَ فَعْلَتَكَ ٱلَّتِى فَعَلْتَ وَأَنتَ مِنَ ٱلْكَـٰفِرِينَ ١٩}

\textit{"And you did that thing of yours that you did..."}

What did he do? 

He killed someone. 

He doesn't come out and say, you killed a guy. He said, that thing you did? Then I'm not telling everybody else here, but you know what you did, right? Look at the irony. Firaun is calling Musa\as{} kafir. 

And what the kafir here means is you're in denial. Are you denying it? Are you denying what you did? Now Musa\as{} came with how many points? Please remember how many points? 

Two points. 

Firaun has addressed how many of those points? 

None of them. 

Firaun is a genius man, evil genius. He completely changed the subject. And he came out attacking. And he came out and he said, now let's make a list of what he said. 

Number one, weren't you raised there as a baby? 

Number two, and by the way, calling him a baby makes him feel like he's nothing. Then didn't you live many years here? He's making him feel like, where's your loyalty? This is your house. You should have more respect for the owner of this house. You spent many years here. 

What's the third thing he brought up? You did that thing that you did? The crime. Are you denying it? 

Now Musa\as{} has to respond to all of these allegations. All of these things that he said. But remember that Musa\as{} did not come here for a question answer session. Musa\as{} came here on a command from Allah to talk about two things. 

\begin{itemize}
    \item Number one, that he's a messenger
    \item Number two, that he needs to let? Bani Israel go
\end{itemize}

But of the things that Firaun brought up, let's go over them. 

\begin{itemize}
    \item Number one, I raised you as a baby
    \item Number two, you spent many years here
    \item Number three, you did what you did
    \item Number four, you're denying it
\end{itemize}

Of these four things, what do you think is the most critical problem? Of the things of the controversies that should be addressed. What's the immediate controversy that needs to be addressed right away? Of the Firaun issues. 

The murder. The murder. 

So Musa\as{} immediately catches that. And he says, 

\textarabic{قَالَ فَعَلْتُهَآ إِذًۭا وَأَنَا۠ مِنَ ٱلضَّآلِّينَ ٢٠} 

\textit{"Musa\as{} replied, “I did it then, lacking guidance."}

He says, yes, I did do that. I'm not denying it. I did do it then. Now he doesn't say, I killed a person. If Firaun is not going to come out and say you killed a person, he won't incriminate himself either. So he'll just say, I did it. I did it at the time. 

And I was confused at the time. I was lost at the time. And as a result of what I did, I ran away from all of you. 

What? All of you? I thought he was only talking to who? Firaun. But all of a sudden, Musa\as{} decides to talk to everybody in the court. The security guards, the ministers, the wasiers, the guy that does the fan thing. Everybody. And he says, I ran away from all the y'all. That's me from Texas talking now. I ran away from all of y'all. 

I ran away from you people when I used to be afraid of you. What is he saying when he says, when I used to be afraid of you? I'm back because I'm not afraid of you anymore. None of you. 

\textarabic{فَفَرَرْتُ مِنكُمْ لَمَّا خِفْتُكُمْ فَوَهَبَ لِى رَبِّى حُكْمًۭا وَجَعَلَنِى مِنَ ٱلْمُرْسَلِينَ ٢١}

\textit{"So I fled from you when I feared you. Then my Lord granted me wisdom and made me one of the messengers."}

And when I left, when I ran away from you, my rub, my master gave me firmness and gave me wisdom and gave me solid decision making. Made me from those who are sent. 

Look at the genius of Musa\as{}. He says, yes, I did commit a murder. But as a result of running away from here, Allah made me a messenger. Which was his point number one, wasn't it? He used Firaun's tangent and turned it around and brought back point number one. He didn't get off topic. 

True genius. 

He told Allah, Ya Allah, I will get frustrated and my tongue will stop moving and Allah told him, don't worry, I got you. 

You watch now what Musa\as{} does. This is incredibly ingenious speech. You know what I'm reminded of when I think of Musa\as{}'s speech? I'm reminded of finding Nemo, I'm not a finding the Nemo. I'm reminded of Kung Fu Panda too. You know at the end when he's getting shot with cannonballs and he takes the cannonball and he inner peace right back. Assalamu al-Dakhili, you know. He does that. Firaun is going to shoot at him and what's he going to do? Turn it back around to exactly what he needs to say. Now watch what he does. 

Musa\as{}. He says, 

\textarabic{وَتِلْكَ نِعْمَةٌۭ تَمُنُّهَا عَلَىَّ أَنْ عَبَّدتَّ بَنِىٓ إِسْرَٰٓءِيلَ ٢٢}

\textit{"How can that be a ‘favour,’ of which you remind me, when it was only because you have enslaved the Children of Israel?”"}

By the way, thanks for that favor you did to me. That is in fact a favor you did for me. What is the favor that he did for him? He raised him as a baby. He spent many years there. I acknowledge. Thanks a lot. You provided housing for me. 

Did you provide me that housing so it could justify enslaving all of the Israelites? 

Whoa. 

That was point number one. 

Two. 

Firaun tried to change the subject altogether. Musa\as{} said, okay, I'll take your change of subject and I'll slap you back with it. And I'll make you feel stupid too. As he's saying, thanks a lot for letting me live in your house. I guess that makes it okay to make an entire nation's slaves. Does that make sense to you? Because it sounds rather stupid to me. Now at this point, it's not only two people talking. There are people in the court that are listening to this. And they at this point are actually kind of confused about what just happened. 

Because nobody should survive this long with Firaun. And by the way, if you have a job under Firaun, please don't raise your hand. If you have a job under Firaun, are you happy with your employer? No. So when your employer is getting insulted or owned a little bit, are you a little happy? So the security guard and the fan guy and the minister is going, I mean, they are kind of getting a kick out of this. This is, nobody gets to talk to him like that and nobody gets to own him like that, 

like, oh snap. 

If they had an iPhone back then, they would have been a recording going on on YouTube. For real man, they would have been like, oh look at this. Firaun owned. It would have been Firowned, you know. Anyway, so this happens and so does that mean you get to enslave the children of Israel? He brought up his two points again, didn't he? Now Firaun doesn't know what to do except he has to engage the actual subject because he knows Musa\as{} won't let it go. He won't let those two points go. So he starts with the first point by making fun of it. 

\textarabic{قَالَ فِرْعَوْنُ وَمَا رَبُّ ٱلْعَـٰلَمِينَ ٢٣}

\textit{"Firaun asked, “And what is ‘the Lord of all worlds’?”"}

He says, what Lord of the world? 

What Master of all nations, what are you talking about? 

He doesn't say who is the Master of all nations. He says, what? What Master of all nations? What Master of all nations? 

Musa\as{} is not deterred by the fact that he's making fun of the idea. He simply answers it as though he asked a serious question, oh you want to know what the Lord of the world is? I'll tell you. 

\textarabic{قَالَ رَبُّ ٱلسَّمَـٰوَٰتِ وَٱلْأَرْضِ وَمَا بَيْنَهُمَآ ۖ إِن كُنتُم مُّوقِنِينَ ٢٤}

\textit{"Musa\as{} replied, “He is the Lord of the heavens and the earth and everything in between, if only you had sure faith.”"}

It is actually the Master of the skies and the earth and whatever is between the skies and the earth, if all of you are looking to be convinced. 

He's not talking to the king now, he's talking to who? Everybody else and by the way that is an insult to a king. When you're in the presence of a king you only speak with the king. So he's defying the king, he's answering back to the king. As he's saying by the way the Master I'm talking about owns the skies and the earth and whatever is in between, this is absolutely important because the Pharaohs they believed in the sun God. They believed that the God of the sun, the God of the skies is the sun and the God of the earth is the children of the sun, the Pharaohs. 

Musa\as{} says by the way my God, my Robb, he owns the sky and he owns the earth and he owns whatever is in between. What you got now, homey? And the rest of them are you people looking to get convinced? Because he seems kind of stupid so maybe I'll talk to the rest of you. 

Firaun at this point says, notice is something and this is actually a serious problem for Firaun. Firaun realizes that at this point he has talked about another God besides himself a couple of times. Three times. Three times. And he expects that the people who work under him believe in himself as God, yes? And if you genuinely believe in a God and somebody else comes and says, no, that's not the real God. Let me tell you about the real God. Shouldn't you be offended? Shouldn't someone from the court get up and say, you can't talk about a Lord like that? You don't talk to Firaun, watch your mouth. What the ironic thing is, nobody in the entire court of Firaun got up and said, hey, you better watch it there. Nobody defended Firaun. As a matter of fact, some people are kind of enjoying this. And some people have become even curious. There is another rub. There is a real rub, really? Who's this rub? Firaun is very angry now not only with Musa\as{}, but also angry with his entire people. 

Why? 

Because none of them are angry. 

\textarabic{قَالَ لِمَنْ حَوْلَهُۥٓ أَلَا تَسْتَمِعُونَ ٢٥}

\textit{"Firaun said to those around him, “Did you hear what he said?”"}

And that's frustrating him. So he says to his crowd, he says, he said to all the people around him, are you people not listening to what he's saying? Why are none of you offended? Hey, why is that you smiling back there? 

Musa\as{}, acts like he didn't even hear it, he keeps going. He says, 

By the way, he's not only your master, he's the master of all of you, and the master of your ancestors to the earliest ones. At this point, he just called, I'm not only representing my own rub, I'm representing the rub of all of you and your ancestors and they believe that their ancestry was sacred. And he says, actually, my master owns all of your ancestry too. He's becoming more and more and more offensive, by the way. Did he get off of his point? Musa\as{}? Who's thrown off and frustrated? If it all is. You see, in the beginning of this conversation, one man walked in from the desert with nothing with a stick in his hand and his brother, who's considered a slave, and one man was sitting on top of a throne in a position of power, and in the middle of this conversation, it seems like the tables have turned, and one man seems to be in a position of controlling the conversation, and the other man seems to be losing control of his own room. 

Doesn't it? 

Allah is changing, balancing the, He's moving the balances of power inside the room, inside the courtroom. And now, He says, 

\textarabic{قَالَ إِنَّ رَسُولَكُمُ ٱلَّذِىٓ أُرْسِلَ إِلَيْكُمْ لَمَجْنُونٌۭ ٢٧}

\textit{"Firaun said mockingly, “Your messenger, who has been sent to you, must be insane.”"}

And he goes to his people, this messenger of yours, Whoa, he called him, not Musa, he said, this messenger of yours. Your messenger. Why did he say that? He said that because it looked like the people in the room were so impressed with Musa\as{}, it almost felt like they have already accepted him as a messenger, so he turns to them and says, by the way, this guy you think is your messenger now, and the 

the one who's apparently been sent to all of you, clearly he's not sent to me, is for all of you, because you seem really interested in him. 

he's crazy, stop listening to him. 

Musa\as{} is calm and says 

\textarabic{قَالَ رَبُّ ٱلْمَشْرِقِ وَٱلْمَغْرِبِ وَمَا بَيْنَهُمَآ ۖ إِن كُنتُمْ تَعْقِلُونَ ٢٨}

\textit{"Musa\as{} responded: “He is the Lord of the east and west, and everything in between, if only you had any sense.”"}

He's also the master of the East and the West, and whatever's in between the East and the West if you people can understand. Now Musa\as{} is gone way too far, you know why? Because the East and the West is where the Sun sets, and the Egyptians used to believe that is the Egyptian Empire, the Sun rises and sets in the Egyptian Empire. And whatever's in between them is the Egyptian land, right? And he says, my master is the true master of the Egyptian land, so if you guys understand what I'm saying, let's just get rid of this idiot and worship the true God. 

So he's asking for a military coup in the middle of this conversation, if it all catches a wind of it. He realizes this conversation isn't just about some faith, this conversation is becoming dangerous for my kingdom. He says, 

\textarabic{قَالَ لَئِنِ ٱتَّخَذْتَ إِلَـٰهًا غَيْرِى لَأَجْعَلَنَّكَ مِنَ ٱلْمَسْجُونِينَ ٢٩}

\textit{"Firaun threatened, “If you take any other god besides me, I will certainly have you imprisoned.”"}

If you take any other God besides me, if you take any other Ilah besides me, I will make sure you are among the people who are imprisoned. I will make sure of it, I swear to it, I'll throw you in prison among others. 

Now it's important that he didn't just say, I will throw you in prison. He said, I will throw you in prison among others. Some others was important to mention because you wanted to instill fear into the people that are in the room. Don't get any ideas. I better not see a Shahada in this room. You understand? 

So Musa\as{} said, I'm realizes that the time to talk is over. If he speaks anymore what's going to happen? He's going to get arrested. He's going to get hauled away. And by the way, before I go on I do have to tell you, I've got to keep track of time, man, this is crazy. I don't know how I'll finish this. But I've got to finish this. 

This is awesome. 

Anyway, what I was going to tell you is that when you have a debate with someone, because this is a debate, isn't it? When you have a debate with someone, and the one that you are debating says, you better shut up or I'll beat you. You better stop talking or I'll throw you in jail. In other words, instead of responding with an argument, you respond with the threat of force. When you respond with a threat of force, you have actually accepted the defeat of your arguments. 

You no longer had any arguments, which is why you could only use the only other weapon you have, which is your force. So the use of force is actually an admission that you are wrong, because your words weren't enough. You couldn't handle it. So now everybody in the room knows that Firaun has been defeated. Firaun has been crushed. In front of his people, in his house, in his court, Musa\as{} says, 

\textarabic{قَالَ أَوَلَوْ جِئْتُكَ بِشَىْءٍۢ مُّبِينٍۢ ٣٠}

\textit{"Musa\as{} responded, “Even if I bring you a clear proof?”"}

Even if I brought you something very clear, I won't talk. I'll just show you something. I've done my work talking to you. I've owned you enough. Will you allow me to show you something Firaun is a little nervous, but he looks around. Musa\as{} does not have a suitcase. But he's going to open up and pull out some equipment and show it to him. All he has is a stick in his hand. He says, 

\textarabic{قَالَ فَأْتِ بِهِۦٓ إِن كُنتَ مِنَ ٱلصَّـٰدِقِينَ ٣١}

\textit{"Firaun demanded, “Bring it then, if what you say is true.”"}

Please. Yeah, why don't you show me something if you're telling the truth? What are you going to show me? 

\textarabic{فَأَلْقَىٰ عَصَاهُ فَإِذَا هِىَ ثُعْبَانٌۭ مُّبِينٌۭ ٣٢}

\textit{"So he threw down his staff and—behold!—it became a real snake."}

So he threw his staff. 

Then all of a sudden it turned into a massive python. There are three descriptions of this snake. We need to consider all three of them. 

\begin{itemize}
    \item Thu'ban describes a python which is large enough to swallow a goat. 
    \item Ha'yah describes a snake that has its fangs sticking out. Ready to bite? 
    \item Ja'an describing a snake that is so terrifying that a person who sees it thinks it's a Jin. 
\end{itemize}

A snake that is massive like a python fangs or sticking out his mouth is open. It doesn't run around with a mouth closed. It runs around with its mouth open and terrifying that when you look at it you think it might be a gin. And by ha'yah it also suggests that it's moving around quickly, shows up and starts running around in the middle of the courtroom. What happens when people see a snake inside a room? And I'm talking about a small garden snake. What happens when people see a garden snake inside a room? 


Let me tell you what happens. When I used to teach, when we moved into our building at the Dream Campus in Texas we had a little bit of a grasshopper problem. And unfortunately the grasshopper has really enjoyed the sister's side. So one time in the middle of class, the teaching class, and one sister, she sees a grasshopper, jumped right on her desk. And 30 women went through one exit at one time. 


That day I knew that when you tell women to exit and they don't exit for 45 minutes, it is not because they are incapable of exiting. It is because there are no grasshoppers involved. Because when I tell my wife, hey, when you go to people's house, hey, time to go home. What happens? Okay, okay, yeah. 45 minutes later, hey, can we go home now? Yeah, yeah, yeah, I'm just putting my shoes on. Alright, move into the car. No, no, you go ahead. Yeah, see how that works out for you. Because a lot of you just go to the car, I'll just wait in the car. Yeah, you sit in the car for about an hour. They're still inside. 

What? 

I didn't even know you were here. 

I didn't even know you had the grasshoppers. 

Anyway, there's a snake indoors. What is going on inside? Can you imagine? Are people just standing there going, oh, that's quite interesting. This is quite remarkable, really. So, people are going nuts. The guy that does the fan thing, has thrown the fan away, the guy that pours the juice for him, has splashed his face. The security guard says, I quit. And he's run away. The ministers are like, oh, oh, oh, oh, oh, and even Firaun is probably climbed up on his chair, right? 

Musa\as{} up until now had owned the entire room with his words. And now he owns the entire room with the miracle that Allah has given him even way beyond. He owned people's ears, now he owns their eyes. And as that is going on, one does a 

\textarabic{وَنَزَعَ يَدَهُۥ فَإِذَا هِىَ بَيْضَآءُ لِلنَّـٰظِرِينَ ٣٣}

\textit{"Then he drew his hand out of his collar and it was shining white for all to see."}

He weighed a lot within now, and he took his hand out and it turns white. 

And everybody's staring at, what? What is it? His hands just turned white. Watch out for the snake. Oh, he's. Now, all the attention is on Musa\as{} and none of the attention is on Firaun. But all. This is really bad for Firaun. This is really, really bad. This situation needs to be brought under control. Now, there are lots of people inside the room, including security guards, janitors, but also, including important people like ambassadors and administrators, like the wazirs, right-hand men, generals, right? Important people are there to, now Firaun is not so worried if the janitor is impressed. And he's really, really worried if who gets impressed. The generals get impressed because, you know, if you live in a dictatorship, the people that the king fears the most or the people that are the highest up in command, because they can slice his neck at any time. He needs to keep them in line. So he says in the next ayah, Allah Azza wa Jalla describes, 

\textarabic{قَالَ لِلْمَلَإِ حَوْلَهُۥٓ إِنَّ هَـٰذَا لَسَـٰحِرٌ عَلِيمٌۭ ٣٤}

\textit{"Firaun said to the chiefs around him, “He is indeed a skilled magician,"}

He spoke exclusively to the chiefs around him, the generals around him. He's not talking to everybody around him. 

A few ayahs before we saw he spoke to everybody around him. And now he says he spoke to the generals around him. And he said this no doubt is clearly a knowledgeable magician who knows what he's doing. No doubt about it. 

So he's calling Musa\as{}. Magician. He's good at magic. But that's not enough to impress or get the kings to listen. The generals to listen. He says 

\textarabic{يُرِيدُ أَن يُخْرِجَكُم مِّنْ أَرْضِكُم بِسِحْرِهِۦ فَمَاذَا تَأْمُرُونَ ٣٥}

\textit{"who seeks to drive you from your land by his magic. So what do you propose?”"}

You know, I think he wants to get you all kicked out of your land by doing his magic. Guys, this is your land. And he wants to kick you out of your land. By the way, this is the first time Firaun called the land, anybody else's land. Because up until now, if you ask him who's land, is it what does he say? This is my land, don't I alone own the kingdom of Egypt? 

And these rivers flow beneath my feet. This is mine and mine alone. This is mine and mine alone. And Musa\as{}. He looks at this. And Firaun now is saying, hey guys, listen, this is our country. We've got to protect our country. He with his magic is going to get you all kicked out of your land. Why don't you tell me what to do? 

Wait, Firaun is telling other people to tell him what to do. That is huge because that is actually an indication that Firaun has become weak. He's become weak. And he knows if the generals don't feel loyalty towards him now, they might revolt against him. So he needs to make them feel special. So for the first time in their lives, the generals are being asked for their opinion. You guys, why don't you tell me what you think? I thought that was one of the generals probably cried. You've never ever heard what I think ever. So they feel a little close to him and he's keeping them loyal and he says to them, they say to him, 

\textarabic{قَالُوٓا۟ أَرْجِهْ وَأَخَاهُ وَٱبْعَثْ فِى ٱلْمَدَآئِنِ حَـٰشِرِينَ ٣٦}

\textit{"They replied, “Let him and his brother wait and dispatch mobilizers to all cities"}

Let this go, and let his brother go too and appoint recruiters, send recruiters, send gatherers in all the cities. 

\textarabic{يَأْتُوكَ بِكُلِّ سَحَّارٍ عَلِيمٍۢ ٣٧}

\textit{"to bring you every skilled magician.”"}


If he's a magician, bring him, bring me expert magicians. Get the best magicians from all the cities, they will bring them back to you and this is how we will respond to his attack. 

\textarabic{فَجُمِعَ ٱلسَّحَرَةُ لِمِيقَـٰتِ يَوْمٍۢ مَّعْلُومٍۢ ٣٨}

\textit{"So the magicians were assembled at the set time on the appointed day."}

The magician started getting gathered from where? All the different cities. Did it happen overnight? No, it happened over weeks. In those weeks, what is Musa\as{} doing? Musa\as{}, his not just sent to Firaun, is he? Who was he sent to? The entire nation. Allah just told him to start with Firaun. So in the meantime, Musa\as{} is going with his message all over Egypt. By the way, inside the courtroom, there are some people who saw this entire drama happen and one of the security guards went home and told his wife what happened. You won't know what happened to the head. And of course, the next day, all of you go to Egypt. So especially because he started with women, I'm telling you something, don't tell anyone. Because she doesn't call her friend and says, listen girl, I'm going to tell you something. Don't tell anybody. And pretty much all of you go to Egypt but no one told anyone else. And as this is happening, whose reputation has gone down the drain? Firaun is humiliated among the people. Oh my God. As Firaun walks by, somebody says, snake. And in the meantime, the message of Musa\as{}, his reputation is growing. And these magicians have been gathered from everywhere and the magicians also hear that Firaun has gone down in the polls. He looks really bad in the elections right now. Everybody's making fun of him. He's not what he used to be. His clout and his fear of Firaun is kind of dying down among the people. They don't think of him as invincible anymore after getting owned by Musa\as{} in his own court. 

So now these magicians, the magicians were gathered for the meeting of a known day, the day of the festival, like their July the 4th or Independence Day, whatever it was, or I guess the Dependence Day because they're under Firaun. But anyway, you know, 

\textarabic{وَقِيلَ لِلنَّاسِ هَلْ أَنتُم مُّجْتَمِعُونَ ٣٩}

\textit{"And the people were asked, “Will you join the gathering,"}

And then Firaun wanted to make sure that this final battle that happens between Musa\as{} and these magicians, this should happen in public with all of the country and everybody should look like they love their nation and they want Musa\as{} to lose even though they don't. So he sends soldiers door to door and he told people, soldiers told people, hey, there's a celebration, a national day of national integrity and security where we're going to defeat the threat against this nation, which is Musa. You are invited to this party, come with your family. Bring a flag with you so you can wave it. 

It was said to the people, are you gathering or what? 

They were forced together to act like they're nationalistic. By the way, does this happen nowadays? Military's come door to door to act like everybody's cheering for the new leader so that the media can show that people love the leader? Does this theatrical performance happen in the world today? Oh yeah, oh yeah. It's not new, it's very pharaonic. And by the way, people still, even though they act like they're cheering for the king, the reality is nobody likes him. 

And by the way, because pharaonic has been looking pretty bad and the day was celebrated as this is the day when the magicians will save our nation and they will fight against the threat to our homeland security. They'll fight against Musa\as{}. When they said that, then they made the magicians look like heroes. Firaun, you know, at the election campaign, his political campaign was to make the magicians look like the nation's heroes. And they look like such great heroes that they started looking better than Firaun. So people started saying to themselves, in the next ayah, 

\textarabic{لَعَلَّنَا نَتَّبِعُ ٱلسَّحَرَةَ إِن كَانُوا۟ هُمُ ٱلْغَـٰلِبِينَ ٤٠}

\textit{"so that we may follow the magicians if they prevail?”"}

Maybe they'll end up following the magicians if they win. Like if they win, it's, it doesn't look like Firaun is going to have power and looks like even maybe the magicians are going to have power. Now Firaun keeps an eye on the politics and he keeps an eye on the news. He has spies everywhere. He hears these conversations happening among the people. He's kind of worried about these magicians now because he brought them, but it's like maybe after they win this election, people might be more interested in them having leadership than even he having leadership. And that's going to create a bigger problem than he originally started with. So these magicians also heard that they're becoming pretty popular. And they're also heard that they are the heroes of the nation that are going to save the nation. 

So these magicians, they're in the locker room after one day of practice and they're talking to each other. And the man was a long day, the rope didn't work. You know? And the other magician says, hey, how much are you getting paid? He says, I'm not getting paid. What are you getting paid? I'm not getting paid either. I was like, should we ask him to get paid? Last time a guy asked him to get paid, he lost his leg. And he gave him his leg as payment. He want to ask him to get paid. And the third guy goes, hey, wait, wait, wait. He needs us. He can't kill us. He's put our posters everywhere. We're on the Facebook page. He can't get rid of us. If there was ever a time to get money out of Firaun, it is now. We should do it, man. Let's go. And the festival is in two hours. He's stuck. Let's mafia Firaun right now. Let's go and kind of squeeze him a little bit. 

So \dots

\textarabic{فَلَمَّا جَآءَ ٱلسَّحَرَةُ قَالُوا۟ لِفِرْعَوْنَ أَئِنَّ لَنَا لَأَجْرًا إِن كُنَّا نَحْنُ ٱلْغَـٰلِبِينَ ٤١} 

\textit{"When the magicians came, they asked Pharaoh, “Shall we have a suitable reward if we prevail?”"}

When the magicians came, they said to Firaun, Hey, Mr. Firaun, we're going to get paid, right? If we're going to win, that we need some motivation, and things might work out. Something might happen. I don't know. Things happen. Something could go wrong. I need a proper motivation. So maybe are we getting paid? Isn't it? Ask a question. Are we really going to get paid? And they're trying to, you know, mafia Firaun, and Firaun, what is he supposed to do at this point? Typically, if people are trying to extort money from him, you should kill them. But he needs them. So he says to them 

\textarabic{قَالَ نَعَمْ وَإِنَّكُمْ إِذًۭا لَّمِنَ ٱلْمُقَرَّبِينَ ٤٢}

\textit{"He replied, “Yes, and you will then certainly be among those closest to me.”"}

Yes, yes, I will give you. And by the way, not only will I give you money, I will make sure that you are among those who are brought close to me, meaning I will give you cabinet positions. You offered them political power also. Why? Because before they develop political aspirations of their own and become the opposition party, let's offer them the vice presidency. See the evil genius? So he said, ah, yeah, I'll make you cabinet ministers and give you money. Okay, now we're properly motivated. So now they go into battle. They're going into battle and then Musa\as{} says, 

\textarabic{قَالَ لَهُم مُّوسَىٰٓ أَلْقُوا۟ مَآ أَنتُم مُّلْقُونَ ٤٣}

\textit{"Musa said to them, “Cast whatever you wish to cast.”"}

Throw whatever it is you're going to throw. Whatever it is, bring it. In other words, he didn't wait for them. He just spoke out. He said, bring whatever you got. Let's see it. 

\textarabic{فَأَلْقَوْا۟ حِبَالَهُمْ وَعِصِيَّهُمْ وَقَالُوا۟ بِعِزَّةِ فِرْعَوْنَ إِنَّا لَنَحْنُ ٱلْغَـٰلِبُونَ ٤٤}

\textit{"So they cast down their ropes and staffs, saying, “By Firaun's might, it is we who will surely prevail.”"}

So they threw their robes and their rods. Because Firaun was going to pay them and he was going to give them cabinet positions, remember? So Firaun told them, listen, I'm paying you. And I'm hooking you up. So you need to make me look good out there. Because I've been looking pretty bad lately. So when you do your thing, also kind of put in a word for me, promoted by our official sponsor, Firaun. You know? So when they threw their ropes and their rods, they said, by the glory of Firaun, by the authority of Firaun. We are going to be the ones that win. So they were told to make Firaun sound good, because he's been looking pretty bad. 

\textarabic{فَأَلْقَىٰ مُوسَىٰ عَصَاهُ فَإِذَا هِىَ تَلْقَفُ مَا يَأْفِكُونَ ٤٥}

\textit{"Then Musa threw down his staff, and—behold!—it devoured the objects of their illusion!"}

Musa\as{} threw his staff. Now I'm thinking, this is going to be an amazing battle. It's going to be like Rocky and that Russian guy that went on forever. I must break you, remember that guy? It went on forever. But so it's going to go to 20 rounds. But you know what happens? Then all of a sudden, it swallowed everything they had made up in a split second. 

In other words, people were cheering. Yay! Huh? What just, it's gone. It's over. It just, there was no time in between. It just ended. And when it ended, the magicians, they're confused at what just happened and they just drop into sajda, they just drop into sajda, let me tell you what happened with the magicians. There are some rocks when something amazing happens. The rock cracks and water comes out. Do you remember that? That's what the magicians were. They had Iman inside. They just needed a kind of experience that would bring that Iman out. Seeing their work disappear in a split second. These people know magic. And when they know magic, they know what is above and beyond magic. That is above and beyond magic. That is from Allah. I'm done, bro. I was just, pfft. I just found such that. 

Firaun is confused. Is this a lunch break? What's going on? What are you guys doing? They get up from sajda they say, 

\textarabic{قَالُوٓا۟ ءَامَنَّا بِرَبِّ ٱلْعَـٰلَمِينَ ٤٧}

\textit{"They declared, “We now believe in the Lord of all worlds—"}

We believe in the master of all nations and all people. Firaun says, I know, I know you believe in me. But continue. Come up with round two. They say, no stupid 

\textarabic{رَبِّ مُوسَىٰ وَهَـٰرُونَ ٤٨}

\textit{"the Lord of Moses and Aaron.”"}

We believe in the master of Musa\as{} and Haroon\as{}, not you. 

Oh my God, you need to understand the complexity of this problem. Firaun gathered and forced the entire nation to come out to watch this event. And he told the people, he put millions of dollars into this campaign, telling people you must pay attention to the magicians. You must pay attention to the magicians. No matter what you do, don't listen to Musa, listen to the magicians. And then he forced everybody to come and listen to the magicians. And the magicians came out and said, hey everyone, let's believe in Musa. In front of it all, and he's like, what, my entire campaign? What are you doing? Now the only one left to defend his campaign is himself. No one else is on his side. Firaun is the only one alone now. So Firaun uses the only tactic he has. He says, 

\textarabic{قَالَ ءَامَنتُمْ لَهُۥ قَبْلَ أَنْ ءَاذَنَ لَكُمْ ۖ إِنَّهُۥ لَكَبِيرُكُمُ ٱلَّذِى عَلَّمَكُمُ ٱلسِّحْرَ فَلَسَوْفَ تَعْلَمُونَ ۚ لَأُقَطِّعَنَّ أَيْدِيَكُمْ وَأَرْجُلَكُم مِّنْ خِلَـٰفٍۢ وَلَأُصَلِّبَنَّكُمْ أَجْمَعِينَ ٤٩}

\textit{"Firaun threatened, “How dare you believe in him before I give you permission? He must be your master who taught you magic, but soon you will see. I will certainly cut off your hands and feet on opposite sides, then crucify you all.”"}

You believed in him before I gave you people permission? Ah, he is your big chief. I see, I see, I see, the one who taught you magic, he is the one who taught you magic. He knows that Musa\as{} is not the one who taught him magic. He knows that they learn, they learn magic from their own cities. They weren't even in contact with Musa\as{} until the day of. But he's making this up for who, for the crowd. You people will find out soon enough. First I will cut your right arms and left legs or left legs and right legs and left arms. Cut you off from the opposite sides. Then I will hang you and crucify you all together. He said this to them, you know why? He's not worried about them. They're going to die anyway. He's worried about leaving an example for the public. So he wants to leave them hanging in public. So nobody else gets any ideas. And these magicians, they hear this and you know what they say? Once the water comes out, once the iman comes out, it makes you rock solid in split seconds. They turn back to Firaun and they say, 

\textarabic{قَالُوا۟ لَا ضَيْرَ ۖ إِنَّآ إِلَىٰ رَبِّنَا مُنقَلِبُونَ ٥٠}

\textit{"They responded, “That would be no harm! Surely to our Lord we will all return."}

No problem. We're going to return to our master anyway. What you're going to do? You can't hurt us anymore. 

I'm going to stop here. But I will tell you, I shared this dialogue with you to give you just the overall goal of Divine Speech. The goal of Divine Speech is to illustrate to you that the Quran is a living text. That the book describes the narrative in a way that takes you inside a world. You get inside this world and it is an incredible place. And it is unfortunately in my personal opinion so underestimated. So underestimated. The mission of the organization that I started and that I am blessed to have so many colleagues in now alhamdulillah, the mission of this organization is to make the Quran accessible to everybody. And to make the beauty of the Quran known to all the Muslims and all the non-Muslims. My eventual goal is to make Arabic easy to learn for all human beings on this planet. That's what I'd like to do. I would like to make Arabic accessible, the Quran accessible, not only in English, but in Basa, and in Bangladesh, and in Somali, and in Swahili, and in Turkish, and in German. I wanted in every language. I am so very grateful for the love and the appreciation you guys have given myself and all of my team. We are so super grateful to all of you. As you are leaving, please do check out the Bayina TV booth. And finally, if Allah does not give us a chance to meet again, I hope you and I meet in a much, much, much better place. 

BarakAllah wa l-walaikum wa sallamu a'rekum wa rahmatullahi wa l-walaikum.


\end{document}
